Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Doctest reuses the GHCi session for all examples
(not just all examples in a module)
adopting assertRaises.

Doctest reuses the same GHCi session for all examples in a module.
Examples from the same Haddock comment are grouped together,
and share the same scope.
The scope is cleared with \verb|:reload| before a new
Example group is started.

@@

\begin{itemize}
    \item The {\tt testpack} package provides a function that is
        similar in purpose to {\tt shouldThrow}.

        sol: Do you think we should discuss this; or is it safe to
        ignore.

        kazu: Let's add this.

\begin{quote}
\small
\begin{verbatim}
assertRaises :: (Show a, Exception e, Show e, Eq e) =>
  String -> e -> IO a -> IO ()
\end{verbatim}\end{quote}
        But it has several shortcomings:
        \begin{itemize}
            \item
                It only works for exceptions with an {\tt Eq}
                instance, but several standard exceptions (most
                prominently {\tt ErrorCall}) have no {\tt Eq}
                instance.
            \item
                It places an unnecessary {\tt Show} constraint on the
                result of the {\tt IO} action, further limiting it's
                applicability.
            \item
                It only allows to expect specific values; expecting
                any exception of a certain type is not possible.
        \end{itemize}
\end{itemize}

>>>>

Doctest reuses the same GHCi session for all examples.
Examples from the same Haddock comment are grouped together,
and share the same scope.
The scope is cleared with \verb|:reload| before a new
Example group is started.

@@

The {\tt testpack} package provides a function to check
exception, similar to {\tt shouldThrow}.

\begin{quote}
\small
\begin{verbatim}
assertRaises :: (Show a, Exception e, Show e, Eq e) =>
  String -> e -> IO a -> IO ()
\end{verbatim}\end{quote}

\noindent But it has several shortcomings:
It only works for exceptions with an {\tt Eq} instance,
but several standard exceptions (most
prominently {\tt ErrorCall}) have no {\tt Eq} instance.
It places an unnecessary {\tt Show} constraint on the
result of the {\tt IO} action, further limiting it's applicability.
It only allows to expect specific values; expecting
any exception of a certain type is not possible.
